ECCoEs from the Black Box: Letting Models speak for Themselves

### 2023-04-23 paper/paper.tex
trying to sort out the sampling :sob:
working my boi :sunglasses:

\title{ECCCos from the Black Box: Letting Models speak for Themselves}

@@

\subsection{Conformal Counterfactual Explanations}

@@

>>>>

\title{ECCoEs from the Black Box: Letting Models speak for Themselves}

@@

\subsection{ECCoE: Energy-Constrained Conformal Counterfactual Explanation}

@@

\begin{itemize}
  \item BatchNorm does not seem compatible with JEM
  \item Coverage and temperature impacts CCE in somewhat unpredictable ways
  \item It seems that models that are not explicitly trained for generative task, still learn it implictly
  \item Batch size seems to impact quality of generated samples
\end{itemize}
